A Review of the Movie \textit{Apocalypse Now}

### 2015-11-14 paper.tex
Intro rough draft

All basically silent moving on, they arrive at the last US station, the Do Long Bridge, a bridge constantly being destroyed at night, and rebuilt in the day.

>>>>

All basically silent moving on, they arrive at the last US station, the Do Long Bridge, a bridge constantly being destroyed at night, and rebuilt in the day. Willard and Lance begin the search for the commanding officer, slowly realizing the insanity and chaos the men at the bridge have fallen into. Watching the bridge slowly collapse from Vietcong fire, they leave with no fuel or real assistance, and continue the increasingly chaotic path down to Kurtz.

Out of nowhere, a barrage of fire consumes the boat, cause panic and return fire. In the heat of the barrage, Clean is downed, and only after, does the rest of the crew. Devastated by the death of their 17 year old comrade, the sullen remaining crew is stopped in the fog by a mysterious by French troops. After speaking with them, they come to an agreement, letting the US crew bury and respectfully say goodbye to Clean. After burying Clean, Willard finds himself at dinner, finding out about the French clan's plantation and how determined they are to stay. After losing World War 1 and 2, the these French demand victory even to death, becoming enraged with Willard and the US, pointing out how they may win every battle, but have no chance to win the war. Nothing can be gained there for the US, and thus drive the families to retire for the evening.

One particular women, Roxanne, stays, and begins connecting with Willard. Roxanne lost her husband, and tells Willard about how she would tell him "There are two of you don't you see? One that kills. One that loves." Willard begins to realize he is exactly that, a man that kills, and one that loves. However his love had been lost, lost when he left his home, became enthralled in the war and lost touch until now, during his time with Roxanne.

On the final stretch to Kurtz, another barrage floods the boat again, except this time of arrows. Chief orders return fire, but after Willard realizes they are just toy arrows, he demands a cease fire. When Chief becomes enraged with the desire of power that Willard has, he turns his back and a spear impales him. As Chief chokes on his own blood, he begins to attempt to choke out Willard, but Willard responds and smothers Chief.

Having lost two men, the crew, only Chef, Lance, and Willard remaining, finally arrive at Kurtz's base. Greeted by a single American photographer and hundreds of Kurtz's followers. Slowly realizing the madness that Kurtz has descended into, ruthlessly murdering people who attempt to defy his reign. While exploring the camp, they come across the practically brainwashed Colby, the last man sent to assassinate Kurtz. As the new servant stares down Willard and Chef, they realize just the extremity these people will go for Kurtz.

They return again, this time Willard and Lance, to talk to Kurtz, and telling Chef to call an airstrike if they do not return. While finally meeting Kurtz in person, Willard is captured and imprisoned, while Lance, having totally lost touch with his surfing reality, becomes one of Kurtz's men. After being tied up, Kurtz returns, dropping the head of Chef, not having gotten the airstrike called in, onto Willard's lap. Willard becomes distraught, realizing the mistakes he has made.

Eventually he is set free, under prohibition, wandering the colony Kurtz has built. While under watch, Kurtz lectures Willard on the reality of war and humanity, reflecting the French plantation words that US can not win with the dedication of the Vietcong.

That night the colony throws a celebration, while Willard sneaks into Kurtz quarters. As Kurtz reads off quotes to send to the US army, Willard attacks him with a machete, eventually forcing Kurtz to the ground. As Kurtz breaths his final breaths, he utters the words "The horror...the horror...". As Willard leaves from Kurtz's quarters, praised by the now aware colony as the new god, and grabs Lance to leave. Finishing with the two leaving the colony  in silence, it begs the question of who is really insane in war, particularly on the can not be won.
